 

### 2021-09-01 vertical-thermal-review.Rmd
added space for NEON table, fixing headers
issues #53 , #54

appendix_NEON_methods_title<- "Methods for NEON vertical profiles"
appendix_tealeaves_methods_title <- "Methods for leaf energy balance modeling"
appendix_lit_review_methods_title<- "Methods for literature review"

#SI table numbers
SItable_example = "S1"

#SI table captions
SItable_example_legend <- "Table S1. ...."

@@

Appendix `r appendix_NEON_methods`. `r appendix_NEON_methods_title`

Appendix `r appendix_tealeaves_methods`. `r appendix_tealeaves_methods_title`

Appendix `r appendix_lit_review_methods`. `r appendix_lit_review_methods_title`

SIfig_example_legend

>>>>

appendix_NEON_methods_title<- "Methods S1. Methods for NEON vertical profiles"
appendix_tealeaves_methods_title <- "Methods S2. Methods for leaf energy balance modeling"
appendix_lit_review_methods_title<- "Methods S3. Methods for literature review"

#SI table numbers
NEON_sites_legend = "S1"
Tealeaves_parameters = "S2"

#SI table captions
NEON_sites_legend = "Table S1. (Neon sites)"
Tealeaves_parameters_legend <- "Table S2. (Tealeaves parameters)"

@@

`r appendix_NEON_methods_title`

`r appendix_tealeaves_methods_title`

`r appendix_lit_review_methods_title`

`r NEON_sites_legend`

`r Tealeaves_parameters_legend`

`r SIfig_NEON_all_legend`

### 2021-09-01 vertical-thermal-review_SI.Rmd
added space for NEON table, fixing headers
issues #53 , #54

appendix_NEON_methods_title<- "Methods for NEON vertical profiles"
appendix_tealeaves_methods_title <- "Methods for leaf energy balance modeling"
appendix_lit_review_methods_title<- "Methods for literature review"

#SI table numbers
Tealeaves_parameters = "S1"

#SI table captions
Tealeaves_parameters_legend <- "Table S1. Tealeaves parameters"

@@

## identification of relevant studies

@@

## criteria for inclusion

@@

>>>>

appendix_NEON_methods_title<- "Methods S1. Methods for NEON vertical profiles"
appendix_tealeaves_methods_title <- "Methods S2. Methods for leaf energy balance modeling"
appendix_lit_review_methods_title<- "Methods S3. Methods for literature review"

#SI table numbers
NEON_sites_legend = "S1"
Tealeaves_parameters = "S2"

#SI table captions
NEON_sites_legend = "Table S1. (Neon sites)"
Tealeaves_parameters_legend <- "Table S2. (Tealeaves parameters)"

@@

## Identification of relevant studies

@@

## Criteria for inclusion

@@

\newpage
 # `r NEON_sites_legend`
